Title Goes Here

### 2021-04-13 analysis/paper/shceof.Rmd
Hace las barras de colores simétricas
Closes #33

```{r eof1-regr-gh, fig.cap = "(ref:eof1-regr-gh-cap)", fig.height=1.2*width_column, fig.width=width_column, dependson="plot_regr"}
plot_regr(regr , "cEOF1", c(200, 50), "hgt") +
  # geom_contour2(data = ~copy(.x)[, estimate := Anomaly(estimate), by = .(term, lev, lat)],
  #              aes(z = estimate, linetype = factor(-sign(..level..))), 
  #              global.breaks = FALSE, breaks = AnchorBreaks(0, bins = 2, exclude = 0)) +
  # scale_linetype(guide = "none") +
  NULL

@@

```{r eof2-regr-gh, fig.cap = "(ref:eof2-regr-gh-cap)", fig.height=1.3*width_column, fig.width=width_column, dependson="plot_regr"}
plot_regr(regr, "cEOF2", c(200, 50), "hgt")

@@

```{r eof1-regr-t, fig.cap = "(ref:eof1-regr-t-cap)",  dependson="plot_regr", fig.height=1.3*width_column, fig.width=width_column}
plot_regr(regr, "cEOF1", c(200, 50), "t")
```

@@

```{r t-vertical, fig.cap = "(ref:t-vertical-cap)", fig.height=2.5, fig.width=width_column}
t %>% 
  .[lat %between% o3wave_lats] %>% 
  .[, .(hgt = weighted.mean(hgt, cos(lat*pi/180)),
        o3 = weighted.mean(o3, cos(lat*pi/180)),
        t = weighted.mean(t, cos(lat*pi/180))), by = .(lev, time, lon)] %>%  
  melt(id.vars = c("lev", "time", "lon")) %>% 
  .[, value := Anomaly(value), by = .(time, lev, variable)] %>%
  .[cut(ceof$eof[[1]], 1)$left, on = "time"] %>% 
  sep_ReIm(format = "wider") %>% 
  .[, ":="(Real = as.numeric(scale(Real)), Imaginary = as.numeric(scale(Imaginary))), by = .(cEOF)] %>% 
  .[, FitLm(value, Real, Imaginary, se = TRUE), by = .(lev, lon, variable)] %>% 
  rm_intercept() %>% 
  .[, term := factor_ReIm(term)] %>% 
  # .[, z := metR:::standard_atmosphere$altitude(lev*100)] %>% 
  # .[, dz1 := c(NA, diff(estimate)/diff(z)) , by = .(term, lon, variable)] %>% 
  # .[, dz2 := c(diff(estimate)/diff(z), NA) , by = .(term, lon, variable)] %>% 
  # .[, dz := (dz1 + dz2)/2] %>% 
  # .[, p.value := Pvaluate(estimate, std.error, df, "fdr"), by = .(term, variable)] %>%
  # .[lev < 900] %>% 
  ggplot(aes(lon, lev)) +
  geom_contour_fill(data = ~.x[variable == "t"],
                    aes(z = estimate, fill = ..level..),
                    breaks = AnchorBreaks(0, binwidth = 0.25, exclude = 0)) +
  geom_contour_tanaka(data = ~.x[variable == "t"],
                      aes(z = estimate),
                      breaks = AnchorBreaks(0, binwidth = 0.25, exclude = 0)) +
  geom_contour2(data = ~.x[variable == "o3"], 
                aes(z = estimate, linetype = factor(-sign(..level..))), 
                breaks = AnchorBreaks(0, exclude = 0)) +
  geom_text_contour(data = ~.x[variable == "o3"], 
                aes(z = estimate*1e9, label = signif(..level.., 2)),
                size = 2,
                skip = 1, stroke = 0.15, stroke.colour = "white", 
                label.placement = lable_placement_min(),
                breaks = AnchorBreaks(0, exclude = 0)) +

  scale_fill_divergent_discretised("Air temperature", guide = guide_colorsteps_bottom(15)) + 
  scale_y_level() +
  scale_linetype(guide = "none") +
  scale_x_longitude(ticks = 60) +
  facet_grid(~term) +
  axis_labs_smol +
  coord_cartesian(clip = "off")
```

@@

  geom_contour_pval(aes(z = p.value)) +
  geom_hline(yintercept = o3wave_lats, size = 0.3, alpha = 0.8) +
  geom_qmap(~.x[lat <= -20]) +
  scale_fill_divergent_discretised("Total Ozone Column", 
                                   guide = guide_colorsteps_bottom(15)) + 
  scale_x_longitude() +
    scale_y_latitude(labels = NULL,
                   minor_breaks = NULL) +
  grid_y +
  scale_linetype(guide = "none") +
  coord_polar() +

@@

  geom_contour_tanaka(aes(z = eof), global.breaks = TRUE, 
                      breaks = AnchorBreaks(0,0.5,  exclude = 0)) +
  scale_fill_divergent_discretised(NULL, guide = guide_colorsteps_bottom()) +
  geom_qmap(~.x[lat <= -20]) +
  scale_x_longitude() +
    scale_y_latitude(labels = NULL,
                   minor_breaks = NULL) +
  grid_y +
  coord_polar() +
  facet_wrap(~EOF, ncol = 3, labeller = labeller(EOF = var)) +
  axis_labs_smol +
  theme(axis.text = element_blank()) +
  tag_facets("rc")
```

@@

```{r sst-psi-2,  fig.cap = "(ref:sst-psi-2-cap)", fig.width = 7, fig.height=4, dependson="plot_sst_psi", fig.env="figure*"}
plot_sst_psi(which_cEOF = "cEOF2", which_lev = 200)

@@

```{r sst-psi-1, fig.cap = "(ref:sst-psi-1-cap)", fig.width = 7, fig.height=4, dependson="plot_sst_psi", fig.env = "figure*"}
plot_sst_psi(which_cEOF = "cEOF1", which_lev = 200)

@@

```{r pp-america, fig.cap = "(ref:pp-america-cap)", fig.width=width_column, fig.height=width_column*1.1}
plot_pp(data = regr_pp, which_cEOF = c("cEOF1", "cEOF2"), which_continent = "america") 
  # annotate("rect", xmin = min(sesa$lon), xmax = max(sesa$lon), 
  #          ymin = min(sesa$lat), ymax = max(sesa$lat),
  #          fill = NA, color = "gray50", size = 0.3)
  #          
```

>>>>

```{r eof1-regr-gh, fig.cap = "(ref:eof1-regr-gh-cap)", fig.height=1.2*width_column, fig.width=width_column, dependson="plot_regr"}
plot_regr(regr , "cEOF1", c(200, 50), "hgt") +
  scale_fill_divergent("Geopotential height", breaks = AnchorBreaks(0, exclude = 0),
                       guide = guide_colorstrip_bottom(15), 
                       limits = c(-1800, 1800))
```

@@

```{r eof2-regr-gh, fig.cap = "(ref:eof2-regr-gh-cap)", fig.height=1.3*width_column, fig.width=width_column, dependson="plot_regr"}
plot_regr(regr, "cEOF2", c(200, 50), "hgt") +
    scale_fill_divergent("Geopotential height", 
                         breaks = AnchorBreaks(0, 200, exclude = 0),
                       guide = guide_colorstrip_bottom(15), 
                       limits = c(-1000+1, 1000-1))
```

@@

```{r eof1-regr-t, fig.cap = "(ref:eof1-regr-t-cap)",  dependson="plot_regr", fig.height=1.3*width_column, fig.width=width_column}
plot_regr(regr, "cEOF1", c(200, 50), "t") +
    scale_fill_divergent("Temperature", breaks = AnchorBreaks(0, exclude = 0),
                       guide = guide_colorstrip_bottom(15), 
                       limits = c(-4.5, 4.5))
```

@@

```{r t-vertical, fig.cap = "(ref:t-vertical-cap)", fig.height=2.5, fig.width=width_column}
t %>% 
  .[lat %between% o3wave_lats] %>% 
  .[, .(hgt = weighted.mean(hgt, cos(lat*pi/180)),
        o3 = weighted.mean(o3, cos(lat*pi/180)),
        t = weighted.mean(t, cos(lat*pi/180))), by = .(lev, time, lon)] %>%  
  melt(id.vars = c("lev", "time", "lon")) %>% 
  .[, value := Anomaly(value), by = .(time, lev, variable)] %>%
  .[cut(ceof$eof[[1]], 1)$left, on = "time"] %>% 
  sep_ReIm(format = "wider") %>% 
  .[, ":="(Real = as.numeric(scale(Real)), Imaginary = as.numeric(scale(Imaginary))), by = .(cEOF)] %>% 
  .[, FitLm(value, Real, Imaginary, se = TRUE), by = .(lev, lon, variable)] %>% 
  rm_intercept() %>% 
  .[, term := factor_ReIm(term)] %>% 
  # .[, z := metR:::standard_atmosphere$altitude(lev*100)] %>% 
  # .[, dz1 := c(NA, diff(estimate)/diff(z)) , by = .(term, lon, variable)] %>% 
  # .[, dz2 := c(diff(estimate)/diff(z), NA) , by = .(term, lon, variable)] %>% 
  # .[, dz := (dz1 + dz2)/2] %>% 
  # .[, p.value := Pvaluate(estimate, std.error, df, "fdr"), by = .(term, variable)] %>%
  # .[lev < 900] %>% 
  ggplot(aes(lon, lev)) +
  geom_contour_fill(data = ~.x[variable == "t"],
                    aes(z = estimate, fill = ..level..),
                    breaks = AnchorBreaks(0, binwidth = 0.3, exclude = 0)) +
  geom_contour_tanaka(data = ~.x[variable == "t"],
                      aes(z = estimate),
                      breaks = AnchorBreaks(0, binwidth = 0.3, exclude = 0)) +
  geom_contour2(data = ~.x[variable == "o3"], 
                aes(z = estimate, linetype = factor(-sign(..level..))), 
                breaks = AnchorBreaks(0, exclude = 0)) +
  geom_text_contour(data = ~.x[variable == "o3"], 
                aes(z = estimate*1e9, label = signif(..level.., 2)),
                size = 2,
                skip = 1, stroke = 0.15, stroke.colour = "white", 
                label.placement = lable_placement_min(),
                breaks = AnchorBreaks(0, exclude = 0)) +

  scale_fill_divergent_discretised("Air temperature", 
                                   # limits = c(-2.25, 2.25),
                                   guide = guide_colorsteps_bottom(15)) + 
  scale_y_level() +
  scale_linetype(guide = "none") +
  scale_x_longitude(ticks = 60) +
  facet_grid(~term) +
  axis_labs_smol +
  coord_cartesian(clip = "off") 
```

@@

  geom_contour_pval(aes(z = p.value)) +
  geom_hline(yintercept = o3wave_lats, size = 0.3, alpha = 0.8) +
  geom_qmap(~.x[lat <= -20]) +
  scale_fill_divergent_discretised("Total Ozone Column", 
                                   limits = c(-30, 30),  
                                   guide = guide_colorsteps_bottom(15)) + 
  scale_x_longitude() +
    scale_y_latitude(labels = NULL,
                   minor_breaks = NULL) +
  grid_y +
  scale_linetype(guide = "none") +
  coord_polar() +

@@

  geom_contour_tanaka(aes(z = eof), global.breaks = TRUE, 
                      breaks = AnchorBreaks(0,0.5,  exclude = 0)) +
  scale_fill_divergent_discretised(NULL, guide = guide_colorsteps_bottom(), 
                                   limits = c(-4, 4)) +
  geom_qmap(~.x[lat <= -20]) +
  scale_x_longitude() +
    scale_y_latitude(labels = NULL,
                   minor_breaks = NULL) +
  grid_y +
  coord_polar() +
  facet_wrap(~EOF, ncol = 3, labeller = labeller(EOF = var)) +
  axis_labs_smol +
  theme(axis.text = element_blank()) +
  tag_facets("rc")
```

@@

```{r sst-psi-2,  fig.cap = "(ref:sst-psi-2-cap)", fig.width = 7, fig.height=4, dependson="plot_sst_psi", fig.env="figure*"}
plot_sst_psi(which_cEOF = "cEOF2", which_lev = 200) +
  scale_fill_divergent_discretised("SST",
                                   limits = c(-1, 1),
                                   guide = guide_colorsteps_bottom(20, order = 2)) 
```

@@

```{r sst-psi-1, fig.cap = "(ref:sst-psi-1-cap)", fig.width = 7, fig.height=4, dependson="plot_sst_psi", fig.env = "figure*"}
plot_sst_psi(which_cEOF = "cEOF1", which_lev = 200) +
  scale_fill_divergent_discretised("SST",
                                   limits = c(-.3, .3),
                                   guide = guide_colorsteps_bottom(20, order = 2)) 
```

@@

```{r pp-america, fig.cap = "(ref:pp-america-cap)", fig.width=width_column, fig.height=width_column*1.1}
plot_pp(data = regr_pp, which_cEOF = c("cEOF1", "cEOF2"), which_continent = "america")  +
  scale_fill_divergent_discretised(NULL, 
                         limits = c(-1, 1),
                         # oob = scales::squish,
                         low = "#8E521C",
                         high = "#00665E",
                         guide = guide_colorsteps_bottom(15)) 
  # annotate("rect", xmin = min(sesa$lon), xmax = max(sesa$lon), 
  #          ymin = min(sesa$lat), ymax = max(sesa$lat),
  #          fill = NA, color = "gray50", size = 0.3)
  #          
```
